Hospital Information Technology and Physician Response

### 2022-03-22 Table Code/overall stats.tex
Updates from Overleaf

\begin{table}[h]
\caption{Summary Statistics}
\centering
\begin{tabular}[t]{lrrrrr}
\toprule
Variable & N & Mean & Std. Dev. & Min & Max\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Outcomes}}\\
\hspace{1em}Ever Retire & 403020 & 0.02 & 0.13 & 0 & 1\\
\hspace{1em}Fraction Patients in Office & 403020 & 0.31 & 0.36 & 0 & 1\\
\hspace{1em}Work in an Office & 403020 & 0.57 & 0.49 & 0 & 1\\
\hspace{1em}Change Zip Codes & 372357 & 0.08 & 0.28 & 0 & 1\\
\hspace{1em}Number of Patients & 403020 & 2220.46 & 3207.08 & 0 & 199765\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Treatment}}\\
\hspace{1em}Exposure to an EHR & 403020 & 0.64 & 0.48 & 0 & 1\\
\hspace{1em}Exposure to an EHR (Low Integration) & 403020 & 0.42 & 0.49 & 0 & 1\\
\hspace{1em}Fraction of Hospitals with EHR & 403020 & 0.52 & 0.46 & 0 & 1\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Characteristics}}\\
\hspace{1em}Age & 403002 & 47.71 & 9.38 & 23 & 89\\
\hspace{1em}Female & 403020 & 0.31 & 0.46 & 0 & 1\\
\hspace{1em}Number of Hospitals Worked With & 403020 & 1.49 & 0.83 & 1 & 20\\
\hspace{1em}Number of Systems Worked With & 403020 & 1.30 & 0.59 & 1 & 8\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[ht]

\caption{Summary Statistics}
\centering
\begin{tabular}[t]{lccccc}
\toprule
Variable & N & Mean & Std. Dev. & Min & Max\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Outcomes}}\\
\hspace{1em}Ever Retire & 337176 & 0.02 & 0.13 & 0 & 1\\
\hspace{1em}Fraction Patients in Office & 337176 & 0.31 & 0.36 & 0 & 1\\
\hspace{1em}Work in an Office & 337176 & 0.57 & 0.49 & 0 & 1\\
\hspace{1em}Change Zip Codes & 313663 & 0.08 & 0.28 & 0 & 1\\
\hspace{1em}Number of Patients & 337176 & 2274 & 3293 & 0 & 199765\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Treatment}}\\
\hspace{1em}Exposure to an EHR & 337176 & 0.76 & 0.43 & 0 & 1\\
\hspace{1em}Exposure to an EHR (Low Integration) & 337176 & 0.51 & 0.50 & 0 & 1\\
\hspace{1em}Fraction of Hospitals with EHR & 337176 & 0.63 & 0.44 & 0 & 1\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Characteristics}}\\
\hspace{1em}Age & 337176 & 47.67 & 9.35 & 23 & 89\\
\hspace{1em}Female & 337176 & 0.31 & 0.46 & 0 & 1\\
\hspace{1em}Number of Hospitals Worked With & 337176 & 1.56 & 0.87 & 1 & 20\\
\hspace{1em}Number of Systems Worked With & 337176 & 1.34 & 0.62 & 1 & 8\\
\bottomrule
\end{tabular}
\label{tab:sumstats1}
\end{table}
